Efficiency

### 2018-01-08 DraftExec.Rnw

There are other some fundamental limitations on the peak efficiency that can be achieved by jets based on simple calculations of ideal efficiency from momentum theory, which are discussed in the next subsection.  They also provide enduring, reliable limitations on the extent to which ingenuity or design changes might be able to improve the efficiency of jets at low speed. But the primary reason why jet efficiencies decline towards zero at low speed is to do with flow separation \parencite{fujisawa1995}, which is what occurs when the assumptions inherent in momentum theory's analysis of an 'ideal' actuator disc start to break down.

@@

Flow separation also tends to lead to unsteady flows, with vortices periodically being shed into the main stream as they are speed up or change shape, and then ingested by the impeller and stator blades.  As can be seen by the diagram in Figure \ref{fig:JetLowFlow.png}, regions abound which are adjacent to or behind flow blockages or reversing flow, where considerable turbulence and unsteady forces would exist.  These effects also have acoustic consequences, which will be discussed in Section \ref{Acoustic Considerations}.

>>>>

There are other some fundamental limitations on the peak efficiency that can be achieved by jets based on simple calculations of ideal efficiency from momentum theory, which are discussed in Section \ref{tradeoffs} (\nameref{tradeoffs}).  They also provide enduring, reliable limitations on the extent to which ingenuity or design changes might be able to improve the efficiency of jets at low speed. But the primary reason why jet efficiencies decline towards zero at low speed is to do with flow separation \parencite{fujisawa1995}, which is what occurs when the assumptions inherent in momentum theory's analysis of an 'ideal' actuator disc start to break down.

@@

Flow separation also tends to lead to unsteady flows, with vortices periodically being shed into the main stream as they are speed up or change shape, and then ingested by the impeller and stator blades.  As can be seen by the diagram in Figure \ref{fig:JetLowFlow.png}, regions abound which are adjacent to or behind flow blockages or reversing flow, where considerable turbulence and unsteady forces would exist.  These effects also have acoustic consequences, which will be discussed in Section \ref{acousticconsiderations} (\nameref{acousticconsiderations}).
